---
title: "Developing Data Products Week 4 Assignment - Pitch Presentation"
author: "tldc01"
date: "June 9, 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Overview

This slide show will introduce you to Pizza Place's Pricing Tool

- What is the app and what is its purpose?
- How does one use the app?
- What does an example look like?

## Purpose

*This application prices a pizza based on the size and toppings selected.*

As it dynamically updates the price based on modifying the options, the user has immediate information avaiable to: 
 - test various scenarios
 - decide which pizza best fits a budget and needs

## Using the Application

1.  Using the sliding scale, select the pizza diameter (in inches).
2.  Choose which topping(s) you want by checking the box next to each option.
3.  The price for your pizza will be displayed on the right hand side window.
4.  You can iteratively go back and modify your pizza; the new price will be reflected.

## Demo

```{r, echo=FALSE}
library(shiny)
sidebarLayout(
    sidebarPanel(
       sliderInput("size", "Select Your Pie Size (Inches - Diameter):", 8, 16, value = 14),
       h3("Now Choose Your Toppings:"),    
       checkboxInput("mushrooms","Mushrooms", value=FALSE),
       checkboxInput("pineapple","Pineapple", value=TRUE),
       checkboxInput("ham","Ham", value=TRUE),
       checkboxInput("sausage","Sausage", value=FALSE),
       checkboxInput("extra_cheese","Extra Cheese", value=FALSE)
    ),

    mainPanel(
        h3("Cost of this Option ($):"),
        calc_price <- renderText(0.8* input$size + 1.25*input$mushrooms + 1.5*input$pineapple + 2.0*input$ham + 1.75*input$sausage + 2.25*input$extra_cheese)
    
        
)
)

```